DeepTriangle: A Deep Learning Approach to Loss Reserving

### 2019-09-06 manuscript/manuscript.Rmd
add references

Deep learning has garnered increasing interest in recent years due to successful applications in many fields [@lecun2015deep] and has recently made its way into the loss reserving literature. @wuthrich2018neural augments the traditional chain ladder method with neural networks to incorporate claims features, @gabrielli2018individual utilizes neural networks to syntheisze claims data, and @gabrielli2018neural and @gabrielli2019neural embeds classical parametric loss reserving models into neural networks.

In developing our framework, which we call DeepTriangle, we also draw inspiration from the existing stochastic reserving literature: @quarg2004munich utilize incurred loss along with paid loss data, @miranda2012double incorporate claim count information in addition to paid losses, and @avanzi2016stochastic consider the dependence between lines of business within an insurer's portfolio.

@@

An alternative approach for evaluation could involve weighting the company results by the associated earned premium or using dollar amounts. However, due to the distribution of company sizes in the dataset, the weights would concentrate on a handful of companies. Hence, to obtain a more balanced evaluation, we choose to report the unweighted percentage-based measures outlined above.

>>>>

Deep learning has garnered increasing interest in recent years due to successful applications in many fields [@lecun2015deep] and has recently made its way into the loss reserving literature. @wuthrich2018neural augments the traditional chain ladder method with neural networks to incorporate claims features, @gabrielli2018individual utilizes neural networks to syntheisze claims data, and @gabrielli2018neural and @gabrielli2019neural embeds classical parametric loss reserving models into neural networks. More specifically, the development in @gabrielli2018neural and @gabrielli2019neural proposes initializing a neural network so that, before training, it corresponds exactly to a classical model, such as the over-dispersed Poisson model. The training iterations then adjust the weights of the neural network to minimize the prediction errors, which can be interpreted as a boosting procedure.

In developing our framework, which we call DeepTriangle, we also draw inspiration from the existing stochastic reserving literature. Works that propose utilizing data in addition paid losses include @quarg2004munich, which uses incurred losses, and @miranda2012double, which incorporates claim count information. Moving beyond a single homogeneous portfolio, @avanzi2016stochastic considers the dependencies among lines of business within an insurer's portfolio, and @peremans2018robust proposes a robust general multivariate chain ladder approach to accommodate outliers. There is also a category of models, referred to as state space or adaptive models, that allow parameters to evolve recursively in time as more data is observed [@chukhrova2017state]. This iterative updating mechanism is analogous to the recurrent neural network architecture presented in this paper.

@@

An alternative approach for evaluation could involve weighting the company results by the associated earned premium or using dollar amounts. However, due to the distribution of company sizes in the dataset, the weights would concentrate on a handful of companies. Hence, to obtain a more balanced evaluation, we choose to report the unweighted percentage-based measures outlined above. We note that the evaluation of reserving models is an ongoing area of research; and refer the reader to @martinek2019analysis for a recent analysis.
